A simple shell model for real-time simulation of intra-ocular implant deployment

### 2009-10-16 ISBMS09/paper.tex
J'ai modifie les valeurs obtenues lors du test theorique et recalcule l'erreur
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@60 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
Ajout de testContatcs.scn pour tester les contacts d'une beam dans un cylindre controle par les shells + mise a jour du papier ISBMS
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@67 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

@@

It can be shown that $z_{max} = 0.126\,q$. We experimentally measured the maximum deflection for different values of pressure $q$ (see table \ref{tab-results}). In average we found $z_{max} = 0.1194\,q $. Hence a $5\,\%$ error between our model and the theory on that test.

\begin{table}[h!]
	\begin{center}
		\begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
		\hline
		 \centering q & \centering 1 & \centering 2 & \centering 3 & \centering 8 \tabularnewline
		\hline
		\centering $z_{max}$ & \centering 0.11 & \centering 0.23 & \centering 0.48 & \centering 1.09 \tabularnewline
		\hline
		\end{tabular}
	\vspace{0.3cm}
	\caption{Experimental results}
	\label{tab-results}
	\end{center}
\end{table}

@@

>>>>

\subsection{Triangular elastic membrane}
The computation of the triangular elastic membrane stiffness matrix can be simply derived from previous works dealing with tetrahedral co-rotational elements (see Muller \emph{et al.} \cite{Muller04}) for instance. The element stiffness matrix $\textbf{K}_e$ can be computed as follows:

\begin{equation}
\textbf{K}_e = \int_v \textbf{J} \boldsymbol\chi \textbf{J}^{T} dV
\end{equation}

where $\textbf{J}$ is the strain-displacement matrix and $\boldsymbol\chi$ embodies the material's behaviour. In the simple case of Hooke's law we have:

\begin{equation}
\boldsymbol\chi = \frac{E}{12(1-\nu^2)}
	\begin{bmatrix}
	1 & \nu & 0 \\
 	\nu & 1 & 0 \\
	0 & 0 & \frac{1}{2} (1-\nu)
	\end{bmatrix}
\end{equation}

The stiffness matrix in the global frame is eventually obtained using the rotation matrix of the element: $\textbf{K} = \textbf{R} \textbf{K}_e \textbf{R}^{T}$.

@@

It can be shown that $z_{max} = 0.126\,q$. We experimentally measured the maximum deflection for different values of pressure $q$ (see table \ref{tab-results}). In average we found $z_{max} = 0.1248\,q $. Hence a $0.93\,\%$ error between our model and the theory on that test.

\begin{table}[h!]
	\begin{center}
		\begin{tabular}{|p{1.7cm}|p{1.7cm}|p{1.7cm}|p{1.7cm}|p{1.7cm}|p{1.7cm}|}
		\hline
		 \centering q & \centering 1 & \centering 2 & \centering 3 & \centering 4 & \centering 5 \tabularnewline
		\hline
		\centering $z_{max}$ & \centering 0.1218 & \centering 0.2475 & \centering 0.3747 & \centering 0.505 & \centering 0.637 \tabularnewline
		\hline
		\end{tabular}
	\vspace{0.3cm}
	\caption{Experimental results}
	\label{tab-results}
	\end{center}
\end{table}

@@

% Ref suction : http://www.coastal-eye-care-maine.com/cataracts-surgery/cataract-surgery-maine.html
